Pyro-Velocity

### 2024-03-25 nbs/index.qmd
nit(nbs): reduce table width Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>
nit(nbs): update description Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

---
title: Pyro-Velocity
description: "Probabilistic modeling of RNA velocity"
format:
  html:
    toc: false

@@

<div style="margin-left: auto; margin-right: auto; max-width: 560px; overflow-x: auto;">

>>>>

---
title: Pyro-Velocity
description: "𝒫robabilistic modeling of RNA velocity ⬱"
format:
  html:
    toc: false

@@

<div style="margin-left: auto; margin-right: auto; max-width: 520px; overflow-x: auto;">
